---
title: "fd_mPRL_Processing_Pipeline"
format: html
editor: visual
---

## 1. Setting Up

```{r}
#| label: setup
#| echo: false


# rm(list=ls())
library(tidyverse)
library(cowplot)

# Point the script to the shared K-Limbic files (read only)
# I find that this can read quite slowly from the RDSF -
# copying over the files locally might speed this process up
# DATA_DIR <- file.path('Z:/',
#                       'K-Limbic'
#                       )


DATA_DIR <- file.path('Z:/',
                      'K-Limbic')

# Output directory, to save figures and files
OUTPUT_DIR <- file.path('Cohort 2/',
                        'Processed Data')
```

##2. SELECT FILES AND MICE

##2.1 SELECT EXPERIMENT
```{r}

# TODO: this needs to be interactive at some point

#decide experiment
experiment<-"mk801_007_coh1"
experiment<-"recent_data"
```

##2.2 FILES/MICE
```{r}
#| label: select files
#| echo: false

#list.files(DATA_DIR)

# Manually hard code the subject IDs
mice <- c(1:24)

# Code in the files to look at
recent_data_files<-c(list.files(DATA_DIR,pattern = "May-2026_Combined.csv"),
                     list.files(DATA_DIR,pattern = "Jun-2026_Combined.csv"))

mk801_007_coh1_files<-c('22-Apr-2026_Combined.csv',
                        '28-Apr-2026_Combined.csv',
                        '01-May-2026_Combined.csv',
                        '06-May-2026_Combined.csv')

files_to_analyse <- c(get(paste0(experiment,"_files")))
```

##3.0 RAW DATA FROM FILES ##3.1 Update Raw Data & save Data is saved as to "Cohort 2/Processed Data" as df_reversal\_<experiment>. Select experiment above. Object in enviroment called df_reversal

```{r}
#| label: read trl


for (FILE in files_to_analyse) {

    if (FILE == files_to_analyse[1]) sessions <- list()

    # For trouble shooting
    # FILE = files_to_analyse[1]

    # Read in all the data from FILE as lines
    # and store in temporary holder, as_lines
    as_lines <- read_lines(file.path(DATA_DIR, FILE))
    
    # Trials start at
    pos_starts <- grep(pattern = TRUE,
                       x = str_starts(string = as_lines,
                                      pattern = 'Ref')
                       ) + 1
    
    # Trials end at
    pos_ends <- grep(pattern = TRUE,
                     x = str_starts(string = as_lines,
                                    pattern = 'ACTIVITYLOG')
                     ) - 2
    
    # Identify relevant rows (indices) for various bits of information 
    pos_Subject_Id <- grep(pattern = TRUE,
                           x = str_starts(string = as_lines,
                                          pattern = 'Subject Id')
                           )
    
    # Set up various place holders
    subjects_in_file <- vector()
    dates_in_file <- vector()
    start_times_in_file <- vector()
    boxes_in_file <- vector()
    databases_in_file <- vector()
    day_tables_in_file <- vector()
    
    
    # TODO: consider improving this solution to get the Subject IDs out
    for (i in 1:length(pos_Subject_Id))  {
      
      # List of subjects
      # as.character not needed, but used to be as.numeric
      subjects_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i]],
                  pattern = ',')[[1]][2]
        )

      # List of start times
      dates_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i] - 16],
                  pattern = ',')[[1]][2]
        )
            
      # List of start times
      start_times_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i] - 15],
                  pattern = ',')[[1]][2]
        )
      
      # List of boxes
      boxes_in_file[i] <- as.integer(
        str_split(string = as_lines[pos_Subject_Id[i] - 14],
                  pattern = ',')[[1]][2]
        )
      
      # List of databases
      databases_in_file[i] <- as.character(
          str_split(string = as_lines[pos_Subject_Id[i] + 1],
                    pattern = ',')[[1]][2]
      )
      
      # List of day tables
      day_tables_in_file[i] <- as.character(
          str_split(string = as_lines[pos_Subject_Id[i] + 3],
                    pattern = ',')[[1]][2]
      )
      
    }
    
    # New for loop
    for (i in 1:length(pos_Subject_Id)) {
    
        # Create temporary holder session
        session <- list()     
        
        ###################################
        # META
        ###################################
        session$meta <- data.frame(
            subj_id    = subjects_in_file[i],
            box        = boxes_in_file[i],
            date       = dates_in_file[i],
            start_time = start_times_in_file[i],
            database   = databases_in_file[i],
            day_table  = day_tables_in_file[i]
        )
        
        ###################################
        # TRIALS
        ###################################
            
        # Extract numeric values from the session's trials
        # TODO: Check compatibility vs. each file type
        # The idea is that this should be fully generic!
        trials_as_list <-
            sapply(X = str_split(as_lines[pos_starts[i]:pos_ends[i]],
                                 pattern = ','),
                   FUN = as.numeric)
        
        # TODO: Check if this is functional or redundant legacy
        # Change to a list, for older style data - check if works for newer!
        if (typeof(trials_as_list) == 'double') {
            trials_as_list <- lapply(seq_len(ncol(trials_as_list)),
                                     function(i) {
                                         trials_as_list[, i]
                                         })
        }
    
        # Extract the numeric values for the list
        # - note we ignore the "start" trial
        for (j in 1:length(trials_as_list[])) {
            
            # Set up empty data frame
            if (j == 1) trials <- data.frame()
            
            # Add the line from the list to the data frame
            # --- as long as it conta data
            if (trials_as_list[[j]][1] != -800) {
                trials <- rbind(trials, trials_as_list[[j]])
                
                # Update the names of the columns
                if (j == length(trials_as_list)) {
                  names(trials) <- paste0("c", 1:dim(trials)[2])
                  }
            }
            
            
            
        }
        
        # Add to session
        session$trials <- trials

        ###################################
        # ACTIVITY LOG
        ###################################
        
        # TODO: Sort out activity log
        session$activity_log <- NA
    
        # Current session data filed into the list of sessions
        sessions[[paste0(subjects_in_file[i], '_',
                         boxes_in_file[i], '_',
                         dates_in_file[i], '_',
                         start_times_in_file[i])]] <- session
        
    }

    
}

##All the trials data from all the sessions covered in files_to_analyse are now neatly stored in the large list object "sessions". Here, each item in the list is another list, named with the subject ID + box + date + time.

# How many sessions in total?
length(sessions)

# Example names of list items 
names(sessions)[1:10]

# Each list item is a list with meta ...
sessions[[1]]$meta

# ... trials
head(sessions[[1]]$trials)

#head(sessions)
# ... and ACTIVITY LOG (just not yet)

#This means we can now start sorting through the sessions and extract the data that we are actually interested in.
# Filters based on your current experiment
# mice_to_analyse <- 1:24
#mice_to_analyse <- 1:24

mk801_007_coh1<-c(2,3,8,10,11,12,14,16,17,18,19,21)
recent_data<-c(1:24)

mice_to_analyse<-get(experiment)

databases_to_analyse <- c('Probabilistsic Reversal',
                          'Probabilistic Reversal')

possible_day_tables<- c(
                            'Nosepoke Active 100',
                           'Reversal Training 6-out-of-6',
                          '[must initiate] Reversal Training 6-out-of-6',
                          '[no initiate] Reversal Training 6-out-of-6',
                          '[must initiate] PRL 6-out-of-6',
                          '[no initiate] PRL 6-out-of-6',
                          '[must initiate] Reversal Training 6 of 6',
                          '[no initiate] Reversal Training 6 of 6',
                          '[must initiate] Probabilistic Reversal 6 of 6',
                          '[no initiate] Probabilistic Reversal 6 of 6')


if (experiment=="recent_data"){
  day_tables_to_analyse<-possible_day_tables
} else {
  
  day_tables_to_analyse <- c('[must initiate] PRL 6-out-of-6',
                          '[no initiate] PRL 6-out-of-6',
                          '[must initiate] Probabilistic Reversal 6 of 6',
                          '[no initiate] Probabilistic Reversal 6 of 6')
  }



sessions_to_analyse <- list()




for (i in 1:length(sessions)) {
    
    # Filter the relevant sessions
    if ((sessions[[i]]$meta$subj_id %in% mice_to_analyse) &&
        (sessions[[i]]$meta$database %in% databases_to_analyse) &&
        (sessions[[i]]$meta$day_table %in% day_tables_to_analyse)) {
        
            # Add session to sessions_to_analyse
            sessions_to_analyse[[names(sessions)[i]]] <- sessions[[i]]
        }
}

length(sessions_to_analyse)

# There are still some steps to go, but these will now be specific for a) each task and b) the version of the K-Limbic output. In either case, we will want to loop through the sessions to read in the relevant information as trials.

###################################
# PRL task
###################################

# Different versions of K-Limbic have different number
# of columns in the output - we can use this information
# to correctly extract the responses!


for (i in 1:length(sessions_to_analyse)) {
    
    if (i == 1) df_reversal <- data.frame()
    
    # Trim the last trial, if no choice was made
    sessions_to_analyse[[i]]$trials <-
        sessions_to_analyse[[i]]$trials %>% filter(!c2 %in% c(128, 150))
    
    # Which format are we looking at?
    n_col <- dim(sessions_to_analyse[[i]]$trials)[2]

    # Pre-glitch-fix (before mid April)
    # Appears as either 59 or 60?
    # TODO: confirm when different number of columns
    if (n_col %in% c(59,60)) {
        df_trials <- cross_join(sessions_to_analyse[[i]]$meta,
                                sessions_to_analyse[[i]]$trials) %>%
            mutate(trial = c1 + 1,
                   chose_left = c38 + c43,
                   chose_right = c39 + c44,
                   reward = c47,
                   left_is_active = as.numeric(c35 > c41),
                   chose_optimal = as.numeric(chose_left == left_is_active),
                   reward_latency = c46 - c45,
                   response_latency = c31 - c30 + c26 - c25,
                   initiate_latency = NA) %>%
            # Select the columns to carry forward - we drop all the columns
            # with raw data from K-Limbic at this point
            dplyr::select(subj_id, box, date, start_time, database, day_table,
                          trial, chose_left, chose_right, reward,
                          left_is_active, chose_optimal,
                          reward_latency, response_latency, initiate_latency)
    }
    
    # This filter might need more conditions
    if (n_col %in% c(64,65)) {
        df_trials <- cross_join(sessions_to_analyse[[i]]$meta,
                                sessions_to_analyse[[i]]$trials) %>%
            mutate(trial = c1 + 1,
                   chose_left = c43 + c48, # Correct 15th April #2
                   chose_right = c44 + c49, # Correct 15th April #2
                   reward = c52,
                   left_is_active = as.numeric(c40 > c45), # Correct 15th April #2
                   chose_optimal = as.numeric(chose_left == left_is_active),
                   reward_latency = c51 - c50,
                   response_latency = c36 - c35 + c31- c30,
                   initiate_latency = NA) %>%
            # Select the columns to carry forward - we drop all the columns
            # with raw data from K-Limbic at this point
            dplyr::select(subj_id, box, date, start_time, database, day_table,
                          trial, chose_left, chose_right, reward,
                          left_is_active, chose_optimal,
                          reward_latency, response_latency, initiate_latency)
    }
    
    df_reversal <-  rbind(df_reversal, df_trials)
    
}


# POSTHOC CALCULATIONS OF ADDITIONAL VARIABLES FROM THE REVERSAL DATA
for (t in 1:dim(df_reversal)[1]) {
    
    # New columns, all filled with NA
    if (t == 1) {
        df_reversal$stay <- NA
        df_reversal$win_stay <- NA
        df_reversal$lose_shift <- NA
        df_reversal$towards_criterion <- NA
        df_reversal$crits <- NA
    }
    
    # All these variables are zero on the first trial of the session
    if (df_reversal$trial[t] == 1) {
        
        df_reversal$win_stay[t] <- 0
        df_reversal$lose_shift[t] <- 0
        df_reversal$stay[t] <- 0
        df_reversal$towards_criterion[t] <- df_reversal$chose_optimal[t]
        df_reversal$crits[t] <- 0
        
    } else if (df_reversal$trial[t] > 1) {
        
        # Stay (regardless of previous outcome)
        df_reversal$stay[t] <- 
            df_reversal$chose_left[t-1] == df_reversal$chose_left[t]
        
        # Win-stay behaviour
        df_reversal$win_stay[t] <- 
            df_reversal$reward[t-1] * df_reversal$stay[t]
        
        # Lose-shift behaviour
        df_reversal$lose_shift[t] <-
            (1 - df_reversal$reward[t-1]) * (1 - df_reversal$stay[t])
        
        # Towards criterion
        df_reversal$towards_criterion[t] <-
            if_else(condition = df_reversal$towards_criterion[t - 1] == 6,
                    true = df_reversal$chose_optimal[t],
                    false = if_else(df_reversal$chose_optimal[t] == 1,
                                    true = df_reversal$towards_criterion[t-1]+1,
                                    false = 0)
                    )
        
        df_reversal$crits[t] <- df_reversal$crits[t-1] +
                                (df_reversal$towards_criterion[t - 1] == 6)
        
    }
    
}

write_csv(x = df_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('df_reversal_',
                                  experiment,
                                  '.csv')
                           )
          )

```

#3.2 Load raw data back into environment

```{r}
df_reversal<-read.csv(paste0(OUTPUT_DIR,"/df_reversal_",experiment,".csv"))
```

##4.0 DATA SUMMARY & LABELLING ##4.1. Summarise data & save

```{r}
# This needs to be updated for the actual names of the schedules
summary_reversal <- 
    df_reversal %>%
    group_by(subj_id,
             day_table,
             date,
             start_time) %>%
    summarise(trials = n(),
              rewards = sum(reward == 1),
              accuracy = mean(chose_optimal,
                              na.rm = TRUE),
              win_stay_prop = sum(win_stay)/sum(reward==1),
              lose_shift_prop = sum(lose_shift)/sum(reward==0),
              stay = mean(stay, na.rm = TRUE),
              reversals = sum(towards_criterion == 6),
              rev_per_100 = reversals/trials*100,
              trials_per_rev = trials/(reversals + 1)) %>%
    mutate(sex = if_else(subj_id %in% c(1:12),
                         true = 'female',
                         false = 'male')) %>%
    # The following code copes with the various incarnations of the task names
    mutate(day_table = factor(
                  day_table,
                  levels = c('[no initiate] Reversal Training 6-out-of-6',
                             '[no initiate] PRL 6-out-of-6',
                             'Reversal Training 6-out-of-6',
                             '[must initiate] Reversal Training 6-out-of-6',
                             '[must initiate] PRL 6-out-of-6',
                             '[must initiate] Reversal Training 6 of 6',
                             '[no initiate] Reversal Training 6 of 6',
                             '[must initiate] Probabilistic Reversal 6 of 6',
                             '[no initiate] Probabilistic Reversal 6 of 6'),
                  labels = c('[no init] Rev Train 6/6',
                             '[no init] PRL 6/6',
                             '[must init] Rev Train 6/6',
                             '[must init] Rev Train 6/6',
                             '[must init] PRL 6/6',
                             '[must init] Rev Train 6/6',
                             '[no init] Rev Train 6/6',
                             '[must init] PRL 6/6',
                             '[no init] PRL 6/6')
                          ))


write_csv(x = summary_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('summary_reversal_',
                                  experiment,
                                  '.csv')
                           )
          )

```

##4.2 Load processed data back into environment

```{r}
summary_reversal<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
```

##4.3. Update Dose Information to csv

```{r}
#experiment<-"mk801_007_coh1"

if (!experiment=="recent_data"){
 doses<-read.csv(paste0(experiment,".csv"))

dates<-doses[1,1:3]

# |>
#   pivot_longer(1:3,
#                names_to = "Day",
#                values_to = "date")



doses<-doses[-1,]|>
  pivot_longer(cols = 4:7,
               values_to = "subj_id")|>
  select(-4)|>
  pivot_longer(cols=1:3,
               names_to = "date",
               values_to = "dose")|>
  mutate(date=recode(date,
                     Day1=dates$Day1,
                     Day2=dates$Day2,
                     Day3=dates$Day3),
         dose=recode(dose,
                     A="Saline",
                     B="0.1",
                     C="0.05"))|>
  mutate(date=as.Date(date,format = "%d/%m/%Y"))




coh_01_007<-c(2,3,8,10,11,12,14,16,17,18,19,21)


for (i in 1:dim(doses)[1]){
  if (!doses$subj_id[i] %in% coh_01_007){
    doses$dose[i]<-NA
  }
}

extra<-read.csv(paste0(experiment,"_extra.csv"))

extra<-extra|>
  mutate(date=as.Date(date,format = "%d/%m/%Y"),
         dose=recode(dose,
                     A="Saline",
                     B="0.1",
                     C="0.05"))

#############USE LEFT JOIN FOR THIS
for (i in 1:dim(extra)[1]) {
  
  extra_mouse<-filter(doses,
               dose==extra$dose[i],
               subj_id==extra$subj_id[i])
  
  extra_mouse$dose<-NA
  
  doses<-filter(doses,
         !(dose==extra$dose[i] &
             subj_id==extra$subj_id[i]))
  
  doses<-bind_rows(doses,extra_mouse)
  
}

doses<-bind_rows(doses,extra)

#get rid of cohort 2 or partial dose days
doses<-filter(doses,
       !is.na(dose))

write_csv(x = doses,
          file = file.path(OUTPUT_DIR,
                           paste0(experiment,
                                  '_doses.csv')
          )
) 
}

```

##4.4. Assign doses to raw data & update data file

```{r}
if (!experiment=="recent_data"){#OUTPUT_DIR<-"Cohort 2/Processed Data"
#see which data/ doses you have
list.files(OUTPUT_DIR)

#get data you want to assign doses to
prl_data<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
#get doses
doses<-read.csv(paste0(OUTPUT_DIR,"/",experiment,"_doses.csv"))

#make sure dates are in the same format, this might need tweaking depending on
#input
prl_data$date<-as.Date(dmy(prl_data$date))
doses$date<-as.Date(doses$date)

# doses$date<-dmy(doses$date)

prl_data<-left_join(x = prl_data,
          y=doses,
          by=c("date","subj_id"))

write_csv(x = summary_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('summary_reversal_',
                                  experiment,
                                  '.csv')
                           )
)
}



```

##5.0.  Plot Data

#5.1 Experimental Dose Response

```{r}

prl_data<-filter(prl_data,
                         !is.na(dose))

prl_data$dose<-factor(prl_data$dose,levels = c("Saline","0.05","0.1"),labels = c("Saline","0.05","0.1"))

prl_data$subj_id<-factor(prl_data$subj_id)


prl_data|>
  ggplot(aes(x=dose,y=lose_shift_prop))+
  geom_boxplot()+
  facet_grid(~day_table)+
  geom_point(aes(group=subj_id,colour=subj_id))+
  geom_line(aes(group=subj_id,colour=subj_id))

```
##5.2 Recent Data
```{r}

summary_reversal$date<-dmy(summary_reversal$date)
mk801_007_coh1<-c(2,3,8,10,11,12,14,16,17,18,19,21)
summary_reversal$cohort<-NA


for (i in 1:dim(summary_reversal)[1]){
  if (summary_reversal$subj_id[i] %in% mk801_007_coh1){
    summary_reversal$cohort[i]<-"Cohort1"
  } else {summary_reversal$cohort[i]<-"Cohort2"}
}

param<-"win_stay_prop"
summary_reversal|>
  filter(cohort=="Cohort2",
         date>"2026-06-01")|>
  ggplot(aes(x=date,y=get(param),group = subj_id,colour = as.factor(subj_id)))+
  facet_grid(cohort~day_table)+
  scale_y_continuous(limits = c(0, 1))  +  # <--- inverted x axis with "day_table_sessions_ago"
  geom_hline(yintercept = c(0.5, 0.8),
             linetype = 'dashed',
             colour = 'magenta',
             linewidth = 0.5)+  # <--- inverted x axis with "day_table_sessions_ago"
  geom_hline(yintercept = c(0.7),
             linetype = 'dashed',
             colour = 'blue',
             linewidth = 0.5) +
  theme_bw()  +
  theme(legend.position = 'right',
        legend.direction = 'vertical') +
  labs(title = 'Reversal training in BJA007 mice')+
  geom_line(aes(y = get(param))) +
  geom_point(aes(y = get(param)), alpha = 0.2, size = 3)+
  ylab(paste0(param))


```



8.  Analyse Data
