---
title: "fd_mPRL_Processing_Pipeline"
format: html
editor: visual
---

## 1. Setting Up

```{r}
#| label: setup
#| echo: false


rm(list=ls())
library(tidyverse)
library(cowplot)

# Point the script to the shared K-Limbic files (read only)
# I find that this can read quite slowly from the RDSF -
# copying over the files locally might speed this process up
# DATA_DIR <- file.path('Z:/',
#                       'K-Limbic'
#                       )
#DRIVE PATH: \\rdsfcifs.acrc.bris.ac.uk
DATA_DIR<-"\\rdsfcifs.acrc.bris.ac.uk/K-Limbic"
DATA_DIR <- file.path('Z:/',
                      'K-Limbic')

# Output directory, to save figures and files
OUTPUT_DIR <- file.path('Cohort 2/',
                        'Processed Data')
```

------------------------------------------------------------------------

##2. SELECT FILES AND MICE

##2.1 SELECT EXPERIMENT

```{r}

# TODO: this needs to be interactive at some point

#decide experiment
experiment<-"mk801_007_coh1"
experiment<-"mk801_007_comb"
experiment<-"recent_data"
```

##2.2 FILES/MICE

```{r}
#| label: select files
#| echo: false

#list.files(DATA_DIR)

# Manually hard code the subject IDs
mice <- c(1:24)

# Code in the files to look at
recent_data_files<-c(
  #list.files(DATA_DIR,pattern = "May-2026_Combined.csv"),
   #                  list.files(DATA_DIR,pattern = "Jun-2026_Combined.csv"),
                      list.files(DATA_DIR,pattern = "Jul2026_Combined.csv"),
                     list.files(DATA_DIR,pattern = "Aug-2026_Combined.csv"))

mk801_007_coh1_files<-c('22-Apr-2026_Combined.csv',
                        '28-Apr-2026_Combined.csv',
                        '01-May-2026_Combined.csv',
                        '06-May-2026_Combined.csv')

mk801_007_comb_files<-c('22-Apr-2026_Combined.csv',
                        '28-Apr-2026_Combined.csv',
                        '01-May-2026_Combined.csv',
                        '06-May-2026_Combined.csv',
                        '25-Jun-2026_Combined.csv',
                        '30-Jun-2026_Combined.csv',
                        '03-Jul2026_Combined.csv')

files_to_analyse <- c(get(paste0(experiment,"_files")))
```

##3.0 RAW DATA FROM FILES ##3.1 Update Raw Data & save Data is saved as to "Cohort 2/Processed Data" as df_reversal\_<experiment>. Select experiment above. Object in enviroment called df_reversal

```{r}
#| label: read trl


for (FILE in files_to_analyse) {

    if (FILE == files_to_analyse[1]) sessions <- list()

    # For trouble shooting
    # FILE = files_to_analyse[1]

    # Read in all the data from FILE as lines
    # and store in temporary holder, as_lines
    as_lines <- read_lines(file.path(DATA_DIR, FILE))
    
    # Trials start at
    pos_starts <- grep(pattern = TRUE,
                       x = str_starts(string = as_lines,
                                      pattern = 'Ref')
                       ) + 1
    
    # Trials end at
    pos_ends <- grep(pattern = TRUE,
                     x = str_starts(string = as_lines,
                                    pattern = 'ACTIVITYLOG')
                     ) - 2
    
    # Identify relevant rows (indices) for various bits of information 
    pos_Subject_Id <- grep(pattern = TRUE,
                           x = str_starts(string = as_lines,
                                          pattern = 'Subject Id')
                           )
    
    # Set up various place holders
    subjects_in_file <- vector()
    dates_in_file <- vector()
    start_times_in_file <- vector()
    boxes_in_file <- vector()
    databases_in_file <- vector()
    day_tables_in_file <- vector()
    
    
    # TODO: consider improving this solution to get the Subject IDs out
    for (i in 1:length(pos_Subject_Id))  {
      
      # List of subjects
      # as.character not needed, but used to be as.numeric
      subjects_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i]],
                  pattern = ',')[[1]][2]
        )

      # List of start times
      dates_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i] - 16],
                  pattern = ',')[[1]][2]
        )
            
      # List of start times
      start_times_in_file[i] <- as.character(
        str_split(string = as_lines[pos_Subject_Id[i] - 15],
                  pattern = ',')[[1]][2]
        )
      
      # List of boxes
      boxes_in_file[i] <- as.integer(
        str_split(string = as_lines[pos_Subject_Id[i] - 14],
                  pattern = ',')[[1]][2]
        )
      
      # List of databases
      databases_in_file[i] <- as.character(
          str_split(string = as_lines[pos_Subject_Id[i] + 1],
                    pattern = ',')[[1]][2]
      )
      
      # List of day tables
      day_tables_in_file[i] <- as.character(
          str_split(string = as_lines[pos_Subject_Id[i] + 3],
                    pattern = ',')[[1]][2]
      )
      
    }
    
    # New for loop
    for (i in 1:length(pos_Subject_Id)) {
    
        # Create temporary holder session
        session <- list()     
        
        ###################################
        # META
        ###################################
        session$meta <- data.frame(
            subj_id    = subjects_in_file[i],
            box        = boxes_in_file[i],
            date       = dates_in_file[i],
            start_time = start_times_in_file[i],
            database   = databases_in_file[i],
            day_table  = day_tables_in_file[i]
        )
        
        ###################################
        # TRIALS
        ###################################
            
        # Extract numeric values from the session's trials
        # TODO: Check compatibility vs. each file type
        # The idea is that this should be fully generic!
        trials_as_list <-
            sapply(X = str_split(as_lines[pos_starts[i]:pos_ends[i]],
                                 pattern = ','),
                   FUN = as.numeric)
        
        # TODO: Check if this is functional or redundant legacy
        # Change to a list, for older style data - check if works for newer!
        if (typeof(trials_as_list) == 'double') {
            trials_as_list <- lapply(seq_len(ncol(trials_as_list)),
                                     function(i) {
                                         trials_as_list[, i]
                                         })
        }
    
        # Extract the numeric values for the list
        # - note we ignore the "start" trial
        for (j in 1:length(trials_as_list[])) {
            
            # Set up empty data frame
            if (j == 1) trials <- data.frame()
            
            # Add the line from the list to the data frame
            # --- as long as it conta data
            if (trials_as_list[[j]][1] != -800) {
                trials <- rbind(trials, trials_as_list[[j]])
                
                # Update the names of the columns
                if (j == length(trials_as_list)) {
                  names(trials) <- paste0("c", 1:dim(trials)[2])
                  }
            }
            
            
            
        }
        
        # Add to session
        session$trials <- trials

        ###################################
        # ACTIVITY LOG
        ###################################
        
        # TODO: Sort out activity log
        session$activity_log <- NA
    
        # Current session data filed into the list of sessions
        sessions[[paste0(subjects_in_file[i], '_',
                         boxes_in_file[i], '_',
                         dates_in_file[i], '_',
                         start_times_in_file[i])]] <- session
        
    }

    
}

##All the trials data from all the sessions covered in files_to_analyse are now neatly stored in the large list object "sessions". Here, each item in the list is another list, named with the subject ID + box + date + time.

# How many sessions in total?
length(sessions)

# Example names of list items 
names(sessions)[1:10]

# Each list item is a list with meta ...
sessions[[1]]$meta

# ... trials
head(sessions[[1]]$trials)

#head(sessions)
# ... and ACTIVITY LOG (just not yet)

#This means we can now start sorting through the sessions and extract the data that we are actually interested in.
# Filters based on your current experiment
# mice_to_analyse <- 1:24
#mice_to_analyse <- 1:24

mk801_007_coh1<-c(2,3,8,10,11,12,14,16,17,18,19,21)
recent_data<-c(1:24)
mk801_007_comb<-c(1:24)

mice_to_analyse<-get(experiment)

databases_to_analyse <- c('Probabilistsic Reversal',
                          'Probabilistic Reversal')

possible_day_tables<- c(
                            'Nosepoke Active 100',
                           'Reversal Training 6-out-of-6',
                          '[must initiate] Reversal Training 6-out-of-6',
                          '[no initiate] Reversal Training 6-out-of-6',
                          '[must initiate] PRL 6-out-of-6',
                          '[no initiate] PRL 6-out-of-6',
                          '[must initiate] Reversal Training 6 of 6',
                          '[no initiate] Reversal Training 6 of 6',
                          '[must initiate] Probabilistic Reversal 6 of 6',
                          '[no initiate] Probabilistic Reversal 6 of 6')


if (experiment=="recent_data"){
  day_tables_to_analyse<-possible_day_tables
} else {
  
  day_tables_to_analyse <- c('[must initiate] PRL 6-out-of-6',
                          '[no initiate] PRL 6-out-of-6',
                          '[must initiate] Probabilistic Reversal 6 of 6',
                          '[no initiate] Probabilistic Reversal 6 of 6')
  }



sessions_to_analyse <- list()




for (i in 1:length(sessions)) {
    
    # Filter the relevant sessions
    if ((sessions[[i]]$meta$subj_id %in% mice_to_analyse) &&
        (sessions[[i]]$meta$database %in% databases_to_analyse) &&
        (sessions[[i]]$meta$day_table %in% day_tables_to_analyse)) {
        
            # Add session to sessions_to_analyse
            sessions_to_analyse[[names(sessions)[i]]] <- sessions[[i]]
        }
}

length(sessions_to_analyse)

# There are still some steps to go, but these will now be specific for a) each task and b) the version of the K-Limbic output. In either case, we will want to loop through the sessions to read in the relevant information as trials.

###################################
# PRL task
###################################

# Different versions of K-Limbic have different number
# of columns in the output - we can use this information
# to correctly extract the responses!


for (i in 1:length(sessions_to_analyse)) {
    
    if (i == 1) df_reversal <- data.frame()
    
    # Trim the last trial, if no choice was made
    sessions_to_analyse[[i]]$trials <-
        sessions_to_analyse[[i]]$trials %>% filter(!c2 %in% c(128, 150))
    
    # Which format are we looking at?
    n_col <- dim(sessions_to_analyse[[i]]$trials)[2]

    # Pre-glitch-fix (before mid April)
    # Appears as either 59 or 60?
    # TODO: confirm when different number of columns
    if (n_col %in% c(59,60)) {
        df_trials <- cross_join(sessions_to_analyse[[i]]$meta,
                                sessions_to_analyse[[i]]$trials) %>%
            mutate(trial = c1 + 1,
                   chose_left = c38 + c43,
                   chose_right = c39 + c44,
                   reward = c47,
                   left_is_active = as.numeric(c35 > c41),
                   chose_optimal = as.numeric(chose_left == left_is_active),
                   reward_latency = c46 - c45,
                   response_latency = c31 - c30 + c26 - c25,
                   initiate_latency = NA) %>%
            # Select the columns to carry forward - we drop all the columns
            # with raw data from K-Limbic at this point
            dplyr::select(subj_id, box, date, start_time, database, day_table,
                          trial, chose_left, chose_right, reward,
                          left_is_active, chose_optimal,
                          reward_latency, response_latency, initiate_latency)
    }
    
    # This filter might need more conditions
    if (n_col %in% c(64,65)) {
        df_trials <- cross_join(sessions_to_analyse[[i]]$meta,
                                sessions_to_analyse[[i]]$trials) %>%
            mutate(trial = c1 + 1,
                   chose_left = c43 + c48, # Correct 15th April #2
                   chose_right = c44 + c49, # Correct 15th April #2
                   reward = c52,
                   left_is_active = as.numeric(c40 > c45), # Correct 15th April #2
                   chose_optimal = as.numeric(chose_left == left_is_active),
                   reward_latency = c51 - c50,
                   response_latency = c36 - c35 + c31- c30,
                   initiate_latency = NA) %>%
            # Select the columns to carry forward - we drop all the columns
            # with raw data from K-Limbic at this point
            dplyr::select(subj_id, box, date, start_time, database, day_table,
                          trial, chose_left, chose_right, reward,
                          left_is_active, chose_optimal,
                          reward_latency, response_latency, initiate_latency)
    }
    
    df_reversal <-  rbind(df_reversal, df_trials)
    
}


# POSTHOC CALCULATIONS OF ADDITIONAL VARIABLES FROM THE REVERSAL DATA
for (t in 1:dim(df_reversal)[1]) {
    
    # New columns, all filled with NA
    if (t == 1) {
        df_reversal$stay <- NA
        df_reversal$win_stay <- NA
        df_reversal$lose_shift <- NA
        df_reversal$towards_criterion <- NA
        df_reversal$crits <- NA
    }
    
    # All these variables are zero on the first trial of the session
    if (df_reversal$trial[t] == 1) {
        
        df_reversal$win_stay[t] <- 0
        df_reversal$lose_shift[t] <- 0
        df_reversal$stay[t] <- 0
        df_reversal$towards_criterion[t] <- df_reversal$chose_optimal[t]
        df_reversal$crits[t] <- 0
        
    } else if (df_reversal$trial[t] > 1) {
        
        # Stay (regardless of previous outcome)
        df_reversal$stay[t] <- 
            df_reversal$chose_left[t-1] == df_reversal$chose_left[t]
        
        # Win-stay behaviour
        df_reversal$win_stay[t] <- 
            df_reversal$reward[t-1] * df_reversal$stay[t]
        
        # Lose-shift behaviour
        df_reversal$lose_shift[t] <-
            (1 - df_reversal$reward[t-1]) * (1 - df_reversal$stay[t])
        
        # Towards criterion
        df_reversal$towards_criterion[t] <-
            if_else(condition = df_reversal$towards_criterion[t - 1] == 6,
                    true = df_reversal$chose_optimal[t],
                    false = if_else(df_reversal$chose_optimal[t] == 1,
                                    true = df_reversal$towards_criterion[t-1]+1,
                                    false = 0)
                    )
        
        df_reversal$crits[t] <- df_reversal$crits[t-1] +
                                (df_reversal$towards_criterion[t - 1] == 6)
        
    }
    
}

df_reversal$reversal<-NA

for (d in 1:dim(df_reversal)[1]){
  if ((d==1)|df_reversal$trial[d]==1){
    df_reversal$reversal[d]<-1
  } else if (df_reversal$towards_criterion[d-1]==6){
    df_reversal$reversal[d]<-df_reversal$reversal[d-1]+1
  } else {df_reversal$reversal[d]<-df_reversal$reversal[d-1]}
}

write_csv(x = df_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('df_reversal_',
                                  experiment,
                                  '.csv')
                           )
          )

```

#3.2 Load raw data back into environment

```{r}
df_reversal<-read.csv(paste0(OUTPUT_DIR,"/df_reversal_",experiment,".csv"))
```

##4.0 DATA SUMMARY & LABELLING ###4.1. Summarise data & save

```{r}
# This needs to be updated for the actual names of the schedules
summary_reversal <- 
    df_reversal %>%
    group_by(subj_id,
             day_table,
             date,
             start_time) %>%
    summarise(trials = n(),
              rewards = sum(reward == 1),
              accuracy = mean(chose_optimal,
                              na.rm = TRUE),
              win_stay_prop = sum(win_stay)/sum(reward==1),
              lose_shift_prop = sum(lose_shift)/sum(reward==0),
              stay = mean(stay, na.rm = TRUE),
              reversals = sum(towards_criterion == 6),
              rev_per_100 = reversals/trials*100,
              trials_per_rev = trials/(reversals + 1)) %>%
    mutate(sex = if_else(subj_id %in% c(1:12),
                         true = 'female',
                         false = 'male')) %>%
    # The following code copes with the various incarnations of the task names
    mutate(day_table = factor(
                  day_table,
                  levels = c('[no initiate] Reversal Training 6-out-of-6',
                             '[no initiate] PRL 6-out-of-6',
                             'Reversal Training 6-out-of-6',
                             '[must initiate] Reversal Training 6-out-of-6',
                             '[must initiate] PRL 6-out-of-6',
                             '[must initiate] Reversal Training 6 of 6',
                             '[no initiate] Reversal Training 6 of 6',
                             '[must initiate] Probabilistic Reversal 6 of 6',
                             '[no initiate] Probabilistic Reversal 6 of 6'),
                  labels = c('[no init] Rev Train 6/6',
                             '[no init] PRL 6/6',
                             '[must init] Rev Train 6/6',
                             '[must init] Rev Train 6/6',
                             '[must init] PRL 6/6',
                             '[must init] Rev Train 6/6',
                             '[no init] Rev Train 6/6',
                             '[must init] PRL 6/6',
                             '[no init] PRL 6/6')
                          ))


write_csv(x = summary_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('summary_reversal_',
                                  experiment,
                                  '.csv')
                           )
          )

```

###4.2 Load processed data back into environment

```{r}
summary_reversal<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
```

###4.3. Update Dose Information to csv

```{r}
#experiment<-"mk801_007_coh1"


if (!experiment=="recent_data"){
 
  doses<-read.csv(paste0(experiment,".csv"))
  coh_01_007<-c(2,3,8,10,11,12,14,16,17,18,19,21)
  coh_02_007<-c(5,6,9,13,22,23,24)


###if just doing cohort 1, can probably use both cohort file for this but
  #sort later
  if (experiment=="mk801_007_coh1"){
    
    dates<-doses[1,1:3]
    doses<-doses[-1,]|>
      pivot_longer(cols = 4:7,
                   values_to = "subj_id")|>
      select(-4)|>
      pivot_longer(cols=1:3,
                   names_to = "date",
                   values_to = "dose")|>
      mutate(date=recode(date,
                         Day1=dates$Day1,
                         Day2=dates$Day2,
                         Day3=dates$Day3),
             dose=recode(dose,
                         A="Saline",
                         B="0.1",
                         C="0.05"))|>
      mutate(date=as.Date(date,format = "%d/%m/%Y"))
    
    
    for (i in 1:dim(doses)[1]){
      if (!doses$subj_id[i] %in% coh_01_007){
        doses$dose[i]<-NA
      }
    }
    } #END JUST COHORT1
  
  if (experiment=="mk801_007_comb"){
    
    dates<-doses[1:2,1:3]
    doses<-doses[-(1:2),]|>
    pivot_longer(cols = 4:7,
                 values_to = "subj_id")|>
    select(-4)|>
    pivot_longer(cols=1:3,
                 names_to = "date",
                 values_to = "dose")|>
    mutate(date=ifelse(subj_id %in% coh_01_007,
                       recode(date,
                              Day1=dates$Day1[1],
                              Day2=dates$Day2[1],
                              Day3=dates$Day3[1]),
                       recode(date,
                              Day1=dates$Day1[2],
                              Day2=dates$Day2[2],
                              Day3=dates$Day3[2])),
           dose=recode(dose,
                       A="Saline",
                       B="0.1",
                       C="0.05"))|>
  mutate(date=as.Date(date,format = "%d/%m/%Y"))

  # extra<-read.csv(paste0(experiment,"_extra.csv"))
  # 
  # extra<-extra|>
  #   mutate(date=as.Date(date,format = "%d/%m/%Y"),
  #          dose=recode(dose,
  #                      A="Saline",
  #                      B="0.1",
  #                      C="0.05"))
  
  
  } #end cohort 2
  
  
  


extra<-read.csv(paste0(experiment,"_extra.csv"))

extra<-extra|>
  mutate(date=as.Date(date,format = "%d/%m/%Y"),
         dose=recode(dose,
                     A="Saline",
                     B="0.1",
                     C="0.05"))

#############USE LEFT JOIN FOR THIS
for (i in 1:dim(extra)[1]) {
  
  extra_mouse<-filter(doses,
               dose==extra$dose[i],
               subj_id==extra$subj_id[i])
  
  extra_mouse$dose<-NA
  
  doses<-filter(doses,
         !(dose==extra$dose[i] &
             subj_id==extra$subj_id[i]))
  
  doses<-bind_rows(doses,extra_mouse)
  
}

doses<-bind_rows(doses,extra)

#get rid of NAs: partial dose days or cohort 2 if excluding
doses<-doses|>
  filter(subj_id %in% c(coh_01_007,coh_02_007),
         !is.na(dose))

doses<-doses|>
  mutate(cohort=ifelse(subj_id %in% coh_01_007,
                         "Cohort1",
                         "Cohort2"))



write_csv(x = doses,
          file = file.path(OUTPUT_DIR,
                           paste0(experiment,
                                  '_doses.csv')
          )
) 
}

```

###4.4. Assign doses to raw data & update data file

```{r}
if (!experiment=="recent_data"){#OUTPUT_DIR<-"Cohort 2/Processed Data"
#see which data/ doses you have
list.files(OUTPUT_DIR)

#get data you want to assign doses to
prl_data<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
df_reversal<-read.csv(paste0(OUTPUT_DIR,"/df_reversal_",experiment,".csv"))


#get doses
doses<-read.csv(paste0(OUTPUT_DIR,"/",experiment,"_doses.csv"))

#make sure dates are in the same format, this might need tweaking depending on
#input
prl_data$date<-as.Date(dmy(prl_data$date))
df_reversal$date<-as.Date(dmy(df_reversal$date))
doses$date<-as.Date(doses$date)

# doses$date<-dmy(doses$date)

prl_data<-left_join(x = prl_data,
          y=doses,
          by=c("date","subj_id"))

prl_data<-prl_data|>
  filter(!is.na(dose))

# df_reversal<-left_join(x = df_reversal,
#           y=doses,
#           by=c("date","subj_id"))
# 
# df_reversal<-filter(df_reversal,
#                  !is.na(dose))

write_csv(x = df_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('df_reversal_',
                                  experiment,
                                  '.csv')
                           )
)

write_csv(x = prl_data,
          file = file.path(OUTPUT_DIR,
                           paste0('summary_reversal_',
                                  experiment,
                                  '.csv')
                           )
)
}



```

###4.5 Trials per reversal

```{r}
df_reversal<-read.csv(paste0(OUTPUT_DIR,"/df_reversal_",experiment,".csv"))

#If reversals hasn't been added:
df_reversal$reversal<-NA

for (d in 1:dim(df_reversal)[1]){
  if ((d==1)|df_reversal$trial[d]==1){
    df_reversal$reversal[d]<-1
  } else if (df_reversal$towards_criterion[d-1]==6){
    df_reversal$reversal[d]<-df_reversal$reversal[d-1]+1
  } else {df_reversal$reversal[d]<-df_reversal$reversal[d-1]}
}

#assign doses to raw data
doses<-read.csv(paste0(OUTPUT_DIR,"/",experiment,"_doses.csv"))


df_reversal<-left_join(x = df_reversal,
          y=doses,
          by=c("date","subj_id"))

df_reversal<-filter(df_reversal,
                 !is.na(dose))

prl_by_rev<-trials_per_rev|>
  group_by(subj_id,date,dose,reversal,day_table)|>
  summarise(crits=sum(towards_criterion==6),
            trials=max(trial),
            crit_per_100=((sum(towards_criterion==6))/max(trial))*100,
            win_stay_prob=(sum(win_stay==1))/sum(reward==1),
            lose_shift_prob=sum(lose_shift==1)/sum(reward==0),
            percent_chose_left=(sum(chose_left==1)/max(trial))*100,
            accuracy=(sum(chose_optimal)/max(trial))*100,#
            n_trials=max(trial),
            trials_to_rev=n()
  )|>mutate(day_table = factor(
                  day_table,
                  levels = c("[must initiate] Probabilistic Reversal 6 of 6",
                             "[no initiate] Probabilistic Reversal 6 of 6" ),
                  labels = c('Must Initiate',
                             'No Initiate')))

write_csv(x = df_reversal,
          file = file.path(OUTPUT_DIR,
                           paste0('trials_per_rev_',
                                  experiment,
                                  '.csv')
                           )
)

write_csv(x = prl_by_rev,
          file = file.path(OUTPUT_DIR,
                           paste0('trials_per_rev_processed',
                                  experiment,
                                  '.csv')
                           )
)


#trials_per_rev<-read.csv(paste0(OUTPUT_DIR,"/trials_per_rev_",experiment,".csv"))
#prl_by_rev<-read.csv(paste0(OUTPUT_DIR,"/trials_per_rev_processed",experiment,".csv"))
```

#5.0. Plot Data

###5.1 Load processed data back into environment

```{r}
summary_reversal<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
```

###5.2 Quick: Experimental Dose Response

```{r}
prl_data<-summary_reversal


prl_data$dose<-factor(prl_data$dose,levels = c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg"))

prl_data$subj_id<-factor(prl_data$subj_id)

names(prl_data)
param<-"rev_per_100"

prl_data|>
  ggplot(aes(x=dose,y=get(param)))+
  geom_boxplot()+
  facet_grid(cohort~day_table)+
  geom_point(aes(group=subj_id,colour=subj_id))+
  geom_line(aes(group=subj_id,colour=subj_id))+
  ylab(paste0(param))

prl_data|>
  ggplot(aes(x=dose,y=lose_shift_prop))+
  geom_boxplot()+
  facet_grid(.~day_table)+
  geom_point(aes(group=subj_id,colour=subj_id))+
  geom_line(aes(group=subj_id,colour=subj_id))+
  ylab(paste0("win_stay_prop"))

prl_data|>
  ggplot(aes(x=dose,y=trials))+
  geom_boxplot()+
  facet_grid(cohort~day_table)+
  geom_point(aes(group=subj_id,colour=subj_id))+
  geom_line(aes(group=subj_id,colour=subj_id))+
  ylab(paste0("trials"))

prl_data|>
  ggplot(aes(x=lose_shift_prop,y=reversals))+
  geom_point()+
  facet_grid(.~dose)+
  geom_smooth()

```

###5.3 Formatted: Experimental Dose Respose

```{r}
prl_data<-summary_reversal
prl_data$dose<-factor(prl_data$dose,levels = c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg"))
prl_data$subj_id<-factor(prl_data$subj_id)
prl_data<-prl_data|>
  mutate(day_table = factor(
                  day_table,
                  levels = c("[must init] PRL 6/6",
                             "[no init] PRL 6/6" ),
                  labels = c('Must Initiate',
                             'No Initiate')))

names(prl_data)
variable<-"lose_shift_prop"
variable<-"rev_per_100"
variable<-"accuracy"
if (variable=="lose_shift_prop"){
  variable_label<-"Lose-Shift Probability"}

if (variable=="rev_per_100"){
  variable_label<-"Reversals per 100 Trials"
}




plot<-
    prl_data|>
    ggplot(mapping=aes(x=dose,
                       y=get(variable)))+
    geom_boxplot(aes(fill=as.factor(dose)),
                 lwd=1,
                 fatten =1)+
    geom_line(mapping=aes(x=dose,
                          y=get(variable),
                          group=subj_id),
              colour="grey",
              alpha=0.5,
              lwd=1)+
    geom_point(mapping = aes(x=dose,
                             y=get(variable),
                             alpha=0.5),
               colour="grey")+
  #  scale_x_continuous(labels=doses, breaks=1:length(doses))+
    xlab("Dose")+
 # ylab(paste0(variable_label))+
    guides(fill="none")+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          #panel.background = element_rect(fill='#EBEBEB'),
          #text=element_text(family="Aptos"),
          #plot.background = element_rect(fill='transparent', colour=NA),
          axis.line = element_line(colour = "black"),
          axis.text.x=element_text(size=20, face="bold",angle=45,colour="black",vjust = 1,hjust = 1),
          axis.text.y=element_text(size=20, face="bold",angle=45,colour="black"),
          axis.title.x = element_text(size=20,face="bold",colour="black"),
          axis.title.y = element_text(size=20,face="bold",colour="black"),
          legend.title = element_text(size = 16,face="bold"),
          legend.text = element_text(size=20),
          legend.position="none",
          strip.text.x = element_text(size=20)
    )+
      scale_fill_manual(values=c('#C3D69B','#B3A2C7','#FFC000'))+
  facet_grid(.~day_table)

if (variable=="rev_per_100"){
  plot<-plot+
    scale_y_continuous(breaks = seq(0,9,1),
                       minor_breaks = 1,
                       limits=c(0,9))
  }

plot
#facet
#bw<-6.75
#bh<-16

# bw<-12
# bh<-28.4
# 
# bw<-13
bh<-16
bw<-23.5

#single
#bh<-16
#bw<-12


plot
 cowplot::save_plot(filename=paste0('Figures/Essay_YR3/',experiment,'/',Sys.Date(),'/',variable,".png"),
                     plot=plot,
                     #bg="transparent,
                     units="cm",
                     base_height =bh,
                     base_width=bw)
plot
```

###5.3 Recent Data

```{r}

summary_reversal$date<-dmy(summary_reversal$date)
mk801_007_coh1<-c(2,3,8,10,11,12,14,16,17,18,19,21)
mk801_007_coh2<-c(5,6,9,13,22,23,24)

summary_reversal$cohort<-NA


for (i in 1:dim(summary_reversal)[1]){
  id<-summary_reversal$subj_id[i]
  if (id %in% mk801_007_coh1){
    summary_reversal$cohort[i]<-"Cohort1"
  } else if (id %in% mk801_007_coh2){
    summary_reversal$cohort[i]<-"Cohort2"} else{
      summary_reversal$cohort[i]<-NA
    }
  
}
names(summary_reversal)
param<-"reversals"
summary_reversal|>
  filter(
    #cohort=="Cohort2",
         day_table=="[must init] Rev Train 6/6"
         #day_table=="[must init] PRL 6/6",
        # date>"2026-06-01"
         )|>
  ggplot(aes(x=date,y=get(param),group = subj_id,colour = as.factor(subj_id)))+
  #facet_grid(cohort~day_table)+
  facet_grid(day_table~subj_id)+
  scale_y_continuous(limits = c(0, 1))  +  # <--- inverted x axis with "day_table_sessions_ago"
  geom_hline(yintercept = c(0.5, 0.8),
             linetype = 'dashed',
             colour = 'magenta',
             linewidth = 0.5)+  # <--- inverted x axis with "day_table_sessions_ago"
  geom_hline(yintercept = c(0.7),
             linetype = 'dashed',
             colour = 'blue',
             linewidth = 0.5) +
  theme_bw()  +
  theme(legend.position = 'right',
        legend.direction = 'vertical') +
  labs(title = 'Reversal training in BJA007 mice')+
  geom_line(aes(y = get(param))) +
  geom_point(aes(y = get(param)), alpha = 0.2, size = 3)+
  ylab(paste0(param))


summary_reversal|>
  filter(!is.na(cohort))|>
  ggplot(aes(x=date,y=reversals,colour=as.factor(subj_id)))+
  geom_line() +
  geom_point(alpha = 0.2, size = 3)+
  geom_hline(yintercept = 4,
             linetype = 'dashed',
             colour = 'magenta',
             linewidth = 0.5)+
  facet_grid(day_table~cohort)

summary_reversal|>
  filter(
    #day_table=="[must init] PRL 6/6",
         is.na(cohort),
         date>"2026-07-20")|>
  ggplot(aes(x=date,y=win_stay_prop,colour=as.factor(subj_id)))+
  geom_line() +
  geom_point(alpha = 0.2, size = 3)+
  geom_hline(yintercept = .7,
             linetype = 'dashed',
             colour = 'magenta',
             linewidth = 0.5)+
  facet_grid(cohort~day_table)



```

###5.4 Trials per reversal

```{r}
###PLot median trials to critetia per reversal
# 
# df_reversal<-read.csv(paste0(OUTPUT_DIR,"/df_reversal_",experiment,".csv"))
# 
# #If reversals hasn't been added:
# df_reversal$reversal<-NA
# 
# for (d in 1:dim(df_reversal)[1]){
#   if ((d==1)|df_reversal$trial[d]==1){
#     df_reversal$reversal[d]<-1
#   } else if (df_reversal$towards_criterion[d-1]==6){
#     df_reversal$reversal[d]<-df_reversal$reversal[d-1]+1
#   } else {df_reversal$reversal[d]<-df_reversal$reversal[d-1]}
# }
# 
# #assign doses to raw data
# doses<-read.csv(paste0(OUTPUT_DIR,"/",experiment,"_doses.csv"))
# 
# 
# df_reversal<-left_join(x = df_reversal,
#           y=doses,
#           by=c("date","subj_id"))
# 
# df_reversal<-filter(df_reversal,
#                  !is.na(dose))
# 
# trials_per_rev<-read.csv(paste0(OUTPUT_DIR,"/trials_per_rev_",experiment,".csv"))
# 
# 
# df_reversal$dose<-factor(df_reversal$dose,levels =c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg") )

#saveit<-prl_by_rev

# prl_by_rev<-trials_per_rev|>
#   group_by(subj_id,date,dose,reversal,day_table)|>
#   summarise(crits=sum(towards_criterion==6),
#             trials=max(trial),
#             crit_per_100=((sum(towards_criterion==6))/max(trial))*100,
#             win_stay_prob=(sum(win_stay==1))/sum(reward==1),
#             lose_shift_prob=sum(lose_shift==1)/sum(reward==0),
#             percent_chose_left=(sum(chose_left==1)/max(trial))*100,
#             accuracy=(sum(chose_optimal)/max(trial))*100,#
#             n_trials=max(trial),
#             trials_to_rev=n()
#   )|>mutate(day_table = factor(
#                   day_table,
#                   levels = c("[must initiate] Probabilistic Reversal 6 of 6",
#                              "[no initiate] Probabilistic Reversal 6 of 6" ),
#                   labels = c('Must Initiate',
#                              'No Initiate')))

#prl_by_rev$day_table
# #prl_by_rev2<-prl_by_rev
# #remoove outliers?
# #create unique labels to delete columns
# prl_by_rev$lab<-1:dim(prl_by_rev)[1]
# #run identify outliers
# test<-(prl_by_rev|>
#          group_by(dose,day_table)|>
#          identify_outliers(trials_to_rev))
# #subset extreme outliers
# test<-subset(test,is.extreme==TRUE)
# #remove outliers
# prl_by_rev <- subset(prl_by_rev, (!lab %in% test$lab))
# #remove identifying column
# prl_by_rev<-
#   prl_by_rev|>
#   select(-lab)
prl_by_rev<-read.csv(paste0(OUTPUT_DIR,"/trials_per_rev_processed",experiment,".csv"))
prl_by_rev$dose<-factor(prl_by_rev$dose,levels =c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg") )


m_prl_sum<-prl_by_rev|>
  group_by(dose,reversal,day_table)|>
  summarise(m_crit_per_100=mean(crit_per_100),
            m_win_stay_prob=mean(win_stay_prob),
            m_lose_shift_prob=mean(lose_shift_prob),
            m_accuracy=mean(accuracy),
            m_crits=mean(crits),
            m_n_trials=mean(n_trials),
            m_trials_to_rev=mean(trials_to_rev),
            median_trials_to_rev=median(trials_to_rev),
            total=n(),
            stdv_trials_to_rev=sd(trials_to_rev)/sqrt(n()))

prl_by_rev$subj_id<-as.factor(prl_by_rev$subj_id)
#reversal_plot<-

plot<-m_prl_sum|>
  filter(reversal<6)|>
  ggplot(mapping=aes(x=reversal,y=median_trials_to_rev,group = dose,colour=dose))+
  ylab("Median Trials To Criteria")

plot<-m_prl_sum|>
  filter(reversal<6)|>
  ggplot(mapping=aes(x=reversal,y=m_trials_to_rev,group = dose,colour=dose))+
  ylab("Mean Trials To Criteria")

reversal_plot<-plot+
  geom_line(linewidth=1,(aes(linetype = dose)))+
  geom_point(size=2,aes(shape=dose))+
  geom_errorbar(aes(ymax=m_trials_to_rev+stdv_trials_to_rev,
                    ymin=m_trials_to_rev-stdv_trials_to_rev),
                width=0,
                linewidth = 1)+
  geom_errorbar(aes(ymax=m_trials_to_rev+stdv_trials_to_rev,
                    ymin=m_trials_to_rev+stdv_trials_to_rev),
                width=0.2,
                linewidth=1)+
  xlab("Reversal") +
  # geom_point(data=prl_sum,
  #            mapping = aes(x=reversal,y=trials_to_rev,colour = dose,shape=subj_id))+
  #scale_colour_brewer(palette = "Dark2",name = "dose")+
  scale_x_continuous(breaks=0:5,
                     minor_breaks = 1)+
  scale_y_continuous(breaks = seq(0,60,5),
                     minor_breaks = 15,
                     limits=c(0,60))+
  #  scale_colour_manual(breaks=c("Saline","0.05mg/kg","0.1mg/kg"),values = c('#C3D69B','#B3A2C7','#FFC000'))+
  theme(
    #panel.grid.major = element_blank(), 
    #  panel.grid.minor = element_blank(),
    #   panel.background = element_blank(),
    #      panel.background = element_rect(fill='#BFCE92'),
    #   text=element_text(family="Aptos"),
    #  plot.background = element_rect(fill='transparent', colour=NA),
    axis.line = element_line(colour = "black"),
    axis.text.x=element_text(face="bold",colour="black",vjust = 1,hjust = 1),
    axis.text.y=element_text(face="bold",colour="black"),
    axis.title.x = element_text(face="bold",colour="black"),
    axis.title.y = element_text(face="bold",colour="black"),
    legend.title = element_text(face="bold"),
    legend.text = element_text(),
   # legend.position = c(0.175, 0.93)
#    legend.position = c(0.175, 0.39)
    legend.position = c(0.84, 0.9)
  )+
  color_palette(c('#C3D69B','#B3A2C7','#FFC000'))+ 
  labs(colour='Dose',shape="Dose",linetype="Dose")+
  #geom_point(data=filter(prl_by_rev,reversal<7),aes(y=trials_to_rev),position = "jitter")+
  facet_grid(day_table~.)

reversal_plot
n_plot<-
  m_prl_sum|>
  filter(reversal<6)|>
  ggplot(mapping=aes(x=reversal,y=total,group = dose,colour=dose))+
  geom_line(linewidth=1,(aes(linetype = dose)))+
  geom_point(size=2,aes(shape=dose))+
  ylab("(n) Mice")+
  xlab("Reversal")+
  scale_x_continuous(breaks=0:5,
                     minor_breaks = 1)+
  scale_y_continuous(breaks = seq(0,12,1),
                     minor_breaks = 1,
                     limits=c(0,12))+
  theme(
    axis.line = element_line(colour = "black"),
    axis.text.x=element_text(face="bold",colour="black",vjust = 1,hjust = 1),
    axis.text.y=element_text(face="bold",colour="black"),
    axis.title.x = element_text(face="bold",colour="black"),
    axis.title.y = element_text(face="bold",colour="black"),
    legend.title = element_text(face="bold"),
    legend.text = element_text(),
    legend.position = c(0.175, 0.615)
  #  legend.position = c(0.85, 0.8)
  #  legend.position = c(0.175, 0.115) #two facet stack
  )+
  color_palette(c('#C3D69B','#B3A2C7','#FFC000'))+ 
  labs(colour='Dose',shape="Dose",linetype="Dose")+
    facet_grid(day_table~.)

n_plot 
bh<-16 #for facet grid
#bh<-9 #for single
bw<-11
  cowplot::save_plot(filename=paste0('Figures/Essay_YR3/',experiment,'/',Sys.Date(),'/ReversalPlot.png'),
                     plot=reversal_plot,
                     #bg="transparent,
                     units="cm",
                     base_height =bh,
                     base_width=bw)
1
  cowplot::save_plot(filename=paste0('Figures/Essay_YR3/',experiment,'/',Sys.Date(),'/n_Plot.png'),
                     plot=n_plot,
                     #bg="transparent,
                     units="cm",
                     base_height =bh,
                     base_width=bw)




```

#8.ANALYSE

###8.1 Load processed data back into environment

```{r}
summary_reversal<-read.csv(paste0(OUTPUT_DIR,"/summary_reversal_",experiment,".csv"))
```

###8.1 2-Way Mixed Anova

```{r}

########Two way mixed ANOVA
#install.packages("rstatix")
library("rstatix")
library("ggpubr")
library("tidyverse")
#rm(list=ls())

summary_reversal<-filter(summary_reversal,
                 !is.na(dose))

summary_reversal$dose<-factor(summary_reversal$dose,levels = c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg"))

variables<-names(summary_reversal)[6:13]

df<-data.frame(matrix(ncol=7,nrow=length(variables)))
names(df)<-c("Variable","initiate","initiate *sig","dose","dose *sig","initiate:dose","initiate:dose *sig")

#variables[8]
i<-4

for (i in 1:length(variables)){
  
  variable<-variables[i]
  
  #create frame
  prl_test<-data.frame(subj_id=summary_reversal$subj_id,
                       initiate=summary_reversal$day_table,
                       dose=summary_reversal$dose,
                       dependent=summary_reversal[[variable]])
  
  ##summary stats
  prl_test|>
    group_by(dose,initiate)|>
    get_summary_stats(dependent,type="mean_sd")
  
  
  ##visualise
  prl_test|>
    ggplot(mapping=aes(x=dose,
                       colour= initiate,
                       y=dependent))+
    geom_boxplot()+
    ylab(variables[i])
  

  
  
  ###Identify and delete outliers
  # #create unique labels to delete columns
  # prl_test$lab<-1:dim(prl_test)[1]
  # #run identify outliers
  # test<-(prl_test|>
  #          group_by(dose,initiate)|>
  #          identify_outliers(dependent))
  # #subset extreme outliers
  # test<-subset(test,is.extreme==TRUE)
  # #remove outliers
  # prl_test <- subset(prl_test, (!lab %in% test$lab))
  # #
  # if (dim(test)[1]>0) {warning("Extreme Outliers!")}
  # 
  # #remove identifying column
  # prl_test<-
  #   prl_test|>
  #   select(-lab)
  # 
  ###Note:none removed for number of trials, 3 moderate outliers for highest group
  
  #check normality
  #1. First plot
  ggplot(prl_test, aes(sample=dependent)) +
    stat_qq() + 
    stat_qq_line()+
    facet_grid(dose~initiate)
  
  
  #2. Then histogram
  prl_test|>
    ggplot(mapping=aes(x=dependent))+
    geom_histogram()+
    facet_grid(dose~initiate)
  
  #3. Finally Shapiro-wilk, want over 0.05
  prl_test|>
    group_by(dose,initiate)|>
    shapiro_test(dependent)
  
  
  #!! its not normal, logit transform
  #prl_test$dependent<-log((prl_test$dependent/(1-prl_test$dependent)))
  #log((x/(1-x)))
  
  #Homogeneity of variance, want over 0.05
  prl_test|>
    group_by(dose)|>
    levene_test(dependent~initiate)
  
  #homogeneity of covariance, want over 0.001
  box_m(prl_test[,"dependent",drop=FALSE],prl_test$initiate)
  
  #Conduct ANOVA
  res.aov <- anova_test(data = prl_test, dv = dependent, wid = subj_id, within = dose ,between = initiate)
  aov.tab<-get_anova_table(res.aov)
  
  
  df$Variable[i]<-variables[i]
  df[i,c(2,4,6)]<-aov.tab$p
  df[i,c(3,5,7)]<-aov.tab$`p<.05`
  
}

df

```

###8.2 Post Hoc Tests

```{r}

####POST-HOC for Two-Way Mixed ANOVA

#prl_test$dependent<-log((prl_test$dependent/(1-prl_test$dependent)))
#log((x/(1-x)))


variable<-variables[7]

prl_test<-data.frame(subj_id=summary_reversal$subj_id,
                     initiate=summary_reversal$day_table,
                     dose=summary_reversal$dose,
                     dependent=summary_reversal[[variable]],
                     cohort=summary_reversal$cohort)

#logit
#prl_test$dependent<-log((prl_test$dependent/(1-prl_test$dependent)))

# prl_test<-prl_test|>
#   filter(cohort=="Cohort2")

##Conduct the ANOVA again
res.aov <- anova_test(data = prl_test, dv = dependent, wid = subj_id, within = dose ,between = initiate)
aov.tab<-get_anova_table(res.aov)
aov.tab

#If there is a significant INTERACTION

one.way <- prl_test |>
  group_by(dose) |>
  anova_test(dv = dependent, wid = subj_id, between = initiate) |>
  get_anova_table() |>
  adjust_pvalue(method = "bonferroni")

pwc<-prl_test|>
  group_by(dose)|>
  pairwise_t_test(dependent~initiate,p.adjust.method = "bonferroni")

prl_test|>
  pairwise_t_test(dependent~dose,p.adjust.method = "bonferroni")


#If there is significant simple main effects you do simple pairwise comparisons
#but i havent done this here
```

###8.3 Formatted Stats plots

```{r}

#this requires the completed ANOVA (initial test) and PWC (post-hoc test) from before

###Boxplot significance
pwc <- pwc |>
  add_xy_position(x = "dose")|>
  filter(!p.adj.signif=="ns")

prl_test|>
  ggplot(mapping=aes(x=dose,
                     y=dependent,
                     group = interaction(dose,initiate)))+
  geom_boxplot()+ 
  stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(aov.tab, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )+
  ylab(variable)

###experiments...

prl_test|>
  ggplot(mapping=aes(x=dose,
                     y=dependent,
                     alpha = initiate,
                     fill=dose))+
  geom_boxplot()+ 
  stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(aov.tab, detailed = TRUE,row = 2),
    caption = get_pwc_label(pwc)
  )+
  ylab(variable)+
      scale_fill_manual(values=c('#C3D69B','#B3A2C7','#FFC000'))



pwc_EDIT<-pwc
pwc_EDIT$xmin<-0.7
pwc_EDIT$xmax<-1.8

###BY PHASE, formatted 


prl_test|>
  ggplot(mapping=aes(x=initiate,
                     y=dependent,
                     group = interaction(dose,initiate),
                     fill=dose))+
  geom_boxplot()+ 
  stat_pvalue_manual(pwc_EDIT) +
  labs(
    subtitle = get_test_label(aov.tab, detailed = TRUE),
    caption = get_pwc_label(pwc_EDIT)
  )+
  ylab(variable)+
      scale_fill_manual(values=c('#C3D69B','#B3A2C7','#FFC000'))








# Not sure what this is...
# variable<-"m_initiate_latency"
# variable<-"n_trials"
# variable<-"accuracy"
# variable<-"m_reward_latency"
# variable<-"m_response_latency"
# variable<-"win_stay_prob"
# variable<-"true_win_stay_prob"
# 
# {prl_test<-data.frame(subj_id=prl_sum$subj_id,
#                       dose=prl_sum$dose,
#                       dependent=prl_sum[[variable]])
#   
#   pwc<-prl_test |>
#     pairwise_t_test(
#       dependent ~ dose, paired = TRUE,
#       p.adjust.method = "bonferroni"
#     )
#   
#   res.aov <- anova_test(data = prl_test, dv = dependent, wid = subj_id, within = dose)
#   
#   pwc <- pwc |>
#     add_xy_position(x = "dose")|>
#     filter(!p.adj.signif=="ns")}

```

###8.5 Trials per reversal Three Way Mixed

```{r}
########Two way mixed ANOVA
#install.packages("rstatix")
library("rstatix")
library("ggpubr")
library("tidyverse")
#rm(list=ls())

prl_by_rev<-read.csv(paste0(OUTPUT_DIR,"/trials_per_rev_processed",experiment,".csv"))
prl_by_rev$dose<-factor(prl_by_rev$dose,levels =c("Saline","0.05","0.1"),labels = c("Saline","0.05mg/kg","0.1mg/kg") )

#create frame
  prl_test<-data.frame(subj_id=prl_by_rev$subj_id,
                       initiate=prl_by_rev$day_table,
                       dose=prl_by_rev$dose,
                       reversal=prl_by_rev$reversal,
                       trials_to_rev=prl_by_rev$trials_to_rev)
#filter
  prl_test<-prl_test|>
    filter(reversal<4)
  
#anova
  res.aov<-anova_test(data=prl_test,
                      dv=trials_to_rev,
                      wid=subj_id,
                      between=initiate,
                      within = c(dose,reversal))
  
  
  get_anova_table(res.aov)
  
  



```
